tablesfigures

### 2015-12-08 manuscript/manuscript_pve.Rmd
text edits
changed dpi=600 on figures

\
```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/allometryplotting.R")
```  
\
**Figure 2.1**. Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.

\
```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/airvars_plotting.R")
```  
\
**Figure 2.2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.

@@

\
```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/allocation_plotting.R")
```  
\
**Figure 2.3**. Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c). For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment. For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.

@@

\
```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/A_stats_plotting.R")
```

@@

\
```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/Amax_TNC_N_plotting2.R")
```  
\
**Figure 2.5**. Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).  Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.  Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen. The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.

@@

\
```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
\
**Figure 2.6**. Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b). For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production. For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.

@@

```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize_scenarios.R")
```

>>>>

\
```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/allometryplotting.R")
```  
\
**Figure 2.1**. Soil volume treatment means &pm; standard error of height growth (a), diameter growth (b), and interpolated seedling leaf area (c) measured weekly of *Eucalyptus tereticornis* seedlings across the experiment duration in 2013.

\
```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/airvars_plotting.R")
```  
\
**Figure 2.2**. Daily maximum and minimum temperature (a), total daily PPFD (b), and daily maximum vapour pressure deficit (c) across the experiment duration in 2013.

@@

\
```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/allocation_plotting.R")
```  
\
**Figure 2.3**. Soil volume treatment means of biomass partitioning to leaves, stems, and roots at harvest (a), bi-variate relationships between mass allocation to leaves and stems + roots (b) and leaf mass as a function of fine root biomass with &pm; standard error (c). For (b) lines represent standardized major axis fitting of the log-transformed allometric relationships of leaf mass fraction by treatment. For (c) the dashed line is the 1:1 relationship and the solid line represents the significant log-log model fit (R^2^ = 0.82) with equation: log(x) = 0.983(log(y)) - 0.036.

@@

\
```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/A_stats_plotting.R")
```

@@

\
```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/Amax_TNC_N_plotting2.R")
```  
\
**Figure 2.5**. Photosynthetic capacity, on a leaf mass basis, as a function of accumulation of leaf starch (a) and leaf nitrogen content without TNC (b).  Colors represent bins levels (n = 5) of both leaf starch and nitrogen grouped from low to high.  Lines represents predictions, for each bin level, from the linear mixed effects model equation of A~mass~ as a function of starch and nitrogen. The marginal R^2^ (fixed effects only) was 0.37 and the conditional R^2^ (fixed and random effects) was 0.48 for the complete model.

@@

\
```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
\
**Figure 2.6**. Total carbon mass for harvested and modeled seedlings versus predicted total carbon gain after 120 days (a) and  reductions in final seedling carbon mass, both modeled and observed, as a function of the reduction in leaf photosynthesis across treatments (b). For (a) the dashed 1:1 identifies the difference between net total leaf carbon gain and gross seedling production. For (b) both seedling carbon mass and daily carbon assimilation were first scaled to the free seedling control.

@@

```{r model_scenarios, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize_scenarios.R")
```

### 2015-12-08 manuscript/tablesfigures_backup.Rmd
changed dpi=600 on figures

```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/allometryplotting.R")
```

@@

```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/airvars_plotting.R")
```

@@

```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/allocation_plotting.R")
```

@@

```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/A_stats_plotting.R")
```

@@

```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/Amax_TNC_N_plotting2.R")
```

@@

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=400, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```

>>>>

```{r allometry, fig.width=6, fig.height=7.8, echo=FALSE,  dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/allometryplotting.R")
```

@@

```{r airvars, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/airvars_plotting.R")
```

@@

```{r allocation, fig.width=6, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/allocation_plotting.R")
```

@@

```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/A_stats_plotting.R")
```

@@

```{r A_tncnitro, fig.width=8, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/Amax_TNC_N_plotting2.R")
```

@@

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```
